---
title: "Get Your Shiny On"
subtitle: "Turning R Code into Interactive Gold!"
date: "2024-12-05"
author: "Tony Galvan"
institute: "Acorns"
format:
  revealjs: 
    theme: acorns.scss
editor: visual
server: shiny
---

## Introduction

-   University of Notre Dame
    -   1999 B.B.A. Management Information Systems
    -   2019 M.S. Data Science
-   Acorns
    -   Data Analyst III & Analytics Engineer
    -   [www.linkedin.com/in/anthony-raul-galvan](https://www.linkedin.com/in/anthony-raul-galvan/)

::: notes
My name is Tony Galván
:::

## Bullets

When you click the **Render** button a document will be generated that includes:

-   Content authored with markdown
-   Output from executable code

```{r}
library(tidyverse)

theme_set(theme_light())

mtcars |>
  ggplot(aes(x = mpg, y = hp, color = disp)) +
  geom_point()
```

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```
